### 2024-11-19 paper.tex
migrate references

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins,
column widths, line spaces, and text fonts are prescribed; please do not
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement
and others are deliberate, using specifications that anticipate your paper
as one part of the entire proceedings, and not as an independent document.
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been
formatted and styled. Do not number text heads---{\LaTeX} will do that
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text,
even after they have been defined in the abstract. Abbreviations such as
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your
equations more compact, you may use the solidus (~/~), the exp function, or
appropriate exponents. Italicize Roman symbols for quantities and variables,
but not Greek symbols. Use a long dash rather than a hyphen for a minus
sign. Punctuate equations with commas or periods when they are part of a
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the
symbols in your equation have been defined before or immediately following
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A
minimum of one author is required for all conference articles. Author names
should be listed starting from left to right and then moving down to the
next line. This is the author sequence that will be used in future citations
and by indexing services. Names should not be listed in columns nor group by
affiliation. Please keep your affiliations as succinct as possible (for
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not
topically subordinate to each other. Examples include Acknowledgments and
References and, for these, the correct style to use is ``Heading 5''. Use
``figure caption'' for your Figure captions, and ``table head'' for your
table title. Run-in heads, such as ``Abstract'', will require you to apply a
style (in this case, italic) in addition to the style provided by the drop
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For
example, the paper title is the primary text head because all subsequent
material relates and elaborates on this one topic. If there are two or more
sub-topics, the next level head (uppercase Roman numerals) should be used
and, conversely, if there are not at least two sub-topics, then no subheads
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
bottom of columns. Avoid placing them in the middle of columns. Large
figures and tables may span across both columns. Figure captions should be
below the figures; table heads should appear above the tables. Insert
figures and tables after they are cited in the text. Use the abbreviation
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4}
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
rather than symbols or abbreviations when writing Figure axis labels to
avoid confusing the reader. As an example, write the quantity
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
units in the label, present them within parentheses. Do not label axes only
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
quantities and units. For example, write ``Temperature (K)'', not
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at
the bottom of the column in which it was cited. Do not put footnotes in the
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use
``et al.''. Papers that have not been published, even if they have been
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
that have been accepted for publication should be cited as ``in press'' \cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English
citation first, followed by the original foreign-language citation \cite{b6}.

\section*{References}
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}

### 2024-12-08 paper.tex
Changes from papeeria

@@
 \usepackage{textcomp}
+\usepackage{lipsum}
 \usepackage{xcolor}
+% \usepackage{todonotes}
+\usepackage{longtable}
+\usepackage{float}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usepgfplotslibrary{polar}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{Analysis of Data Quality Management Maturity Level at PT Bank XYZ\\
+% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
+% should not be used}
+% \thanks{Identify applicable funding agency here. If none, delete this.}
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Filzahanti Nuha Ramadhani}
+\IEEEauthorblockA{
+\textit{Fakultas Ilmu Komputer} \\
+\textit{Universitas Indonesia}\\
+Jakarta, Indonesia \\
+filzahanti.nuha31@ui.ac.id}
+
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\IEEEauthorblockN{2\textsuperscript{rd} Jon Felix Germinian}
+\IEEEauthorblockA{
+\textit{Fakultas Ilmu Komputer} \\
+\textit{Universitas Indonesia}\\
+Jakarta, Indonesia \\
+jon.felix@ui.ac.id}
+
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\IEEEauthorblockN{3\textsuperscript{nd} Samuel Mulatua Jeremy Nainggolan}
+\IEEEauthorblockA{
+\textit{Fakultas Ilmu Komputer} \\
+\textit{Universitas Indonesia}\\
+Jakarta, Indonesia \\
+samuel.mulatua41@ui.ac.id}
 }
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
-or Math in Paper Title or Abstract.
+In the banking industry, high-quality data is essential for operational efficiency, regulatory compliance, and strategic decision-making.
+Understanding the maturity level of Data Quality Management (DQM) is crucial for PT Bank XYZ to identify gaps and uncover opportunities for improvement.
+Poor data quality can lead to significant risks, including inaccurate reporting, flawed decision-making, financial losses, and regulatory penalties.
+This study evaluates the DQM maturity at PT Bank XYZ using David Loshin’s Data Quality Framework and the Data Management Body of Knowledge (DMBOK) guidelines.
+The research involves comprehensive interviews with key stakeholders to assess the bank's performance across eight DQM components, including governance, standards, and technology.
+The findings reveal an average maturity level of 2.04, classified as "Repeatable." While PT Bank XYZ demonstrates strength in data standard aspect, it struggles with deficiencies in data governance, quality protocols, and the implementation of advanced data technologies.
+These gaps hinder the bank’s ability to fully leverage its data assets for strategic growth and regulatory compliance.
+To address these challenges, the study provides actionable recommendations aimed at enhancing DQM practices.
+By adopting these strategies, PT Bank XYZ can improve its data quality framework, reduce risks, and achieve a more sustainable competitive advantage.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+data quality management; maturity model; maturity level; banking data
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Organizations today generate and manage data from a variety of sources, requiring robust systems to handle customer profiles, financial transactions, account management, and credit applications.
+Managing data quality (DQM) has become a critical focus for organizations, particularly in the banking sector, where accurate and reliable data serves as a cornerstone for operational efficiency and strategic growth.
+Poor data quality can lead to inaccuracies that hinder decision-making, such as selecting optimal business locations, and can expose organizations to reputational and financial risks.
 
-\section{Ease of Use}
+In the context of PT Bank XYZ, understanding the maturity level of Data Quality Management (DQM) is crucial to identify gaps and opportunities for improvement.
+The bank operates in a complex data ecosystem, integrating Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and regulatory compliance tools.
+These systems demand high data quality to meet operational needs and comply with regulations, such as POJK No.
+8/2023 on Anti-Money Laundering and Counter Terrorism Financing.
 
-\subsection{Maintaining the Integrity of the Specifications}
+To address these challenges, this paper explores the data quality maturity level of data quality management at PT XYZ and outlines strategies to enhance its governance framework.
+The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands.
 
-The IEEEtran class file is used to format your paper and style the text. All margins,
-column widths, line spaces, and text fonts are prescribed; please do not
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement
-and others are deliberate, using specifications that anticipate your paper
-as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations.
+The study is guided by the following research questions:
+\begin{enumerate}
+    \item What is the current maturity level of data quality management at PT XYZ?
+    \item How can PT XYZ improve its data quality management practices to address regulatory, operational, and strategic risks?
+\end{enumerate}
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a
-separate text file. Complete all content and organizational editing before
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
-proofreading, spelling and grammar.
+\section{Related Works}
 
-Keep your text and graphic files separate until after the text has been
-formatted and styled. Do not number text heads---{\LaTeX} will do that
-for you.
+This section explores three case studies highlighting diverse implementations of Data Quality Management (DQM) and Master Data Management (MDM).
+The first case study, as reported in \cite{dqmBPI2022}, focuses on PT BPI, where financial data quality management faces challenges due to errors, resulting in suboptimal decision-making in the public sector.
+The maturity level is at an initial stage, with reactive efforts managing structured financial data.
+The second case study, detailed in \cite{payani2023}, examines the National Remote Sensing Data Bank (BDPJN), which addresses the management of large volumes of satellite imagery data to support national planning.
+The organization demonstrates a maturity level ranging from defined to managed, handling unstructured remote sensing data.
+Lastly, \cite{hikmawati2021} discusses an MDM-based approach to improve data quality and governance, using the MD3M model to establish a "single source of truth" for transactional, inventory, and employee data.
+This study reflects a higher maturity level with a focus on consistent management of broader datasets, including customer, supplier, and material data.
+These case studies underscore the importance of tailored DQM and MDM practices to address organizational needs and data characteristics.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text,
-even after they have been defined in the abstract. Abbreviations such as
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
-abbreviations in the title or heads unless they are unavoidable.
+\section{Literature Review}
 
-\subsection{Units}
+\subsection{Data Quality}
+
+Data quality is essential for maintaining the usability, reliability, and trustworthiness of data.
+The Data Management Association International (DAMA) has identified six key dimensions of data quality that are widely acknowledged \cite{DAMA_2013} and applied across various fields \cite{wahyudi2023data, kiran2024addressing, antonio2024data}:
+
 \begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+    \item \textbf{Completeness}: This dimension assesses whether all required data is present, ensuring no critical information is missing \cite{mahanti2019data}.
+    \item \textbf{Uniqueness}: Ensures there is no redundant or duplicate data within a dataset, improving the overall integrity \cite{sebastiancoleman2022meeting}.
+    \item \textbf{Timeliness}: Evaluates whether the data is up-to-date and relevant at the time of use, crucial for dynamic and real-time decision-making \cite{mashoufi2023data}.
+    \item \textbf{Validity}: Verifies that the data adheres to predefined formats, business rules, and constraints \cite{mcgilvray2021executing}.
+    \item \textbf{Accuracy}: Measures whether the data accurately represents real-world values or concepts, ensuring trustworthiness \cite{west2021towards}.
+    \item \textbf{Consistency}: Examines whether data values are aligned across multiple datasets or systems, preventing contradictions \cite{antonio2024data}.
 \end{itemize}
 
-\subsection{Equations}
-Number equations consecutively. To make your
-equations more compact, you may use the solidus (~/~), the exp function, or
-appropriate exponents. Italicize Roman symbols for quantities and variables,
-but not Greek symbols. Use a long dash rather than a hyphen for a minus
-sign. Punctuate equations with commas or periods when they are part of a
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+These dimensions are foundational for establishing robust data governance and quality frameworks.
+For instance, studies such as \cite{wahyudi2023data} and \cite{kiran2024addressing} have demonstrated the application of these dimensions in various sectors, including healthcare, smart mobility, and financial institutions.
+Practical approaches to implementing these dimensions are also elaborated in works like \cite{sebastiancoleman2022meeting} and \cite{mahanti2019data}, making them essential for ensuring effective data management strategies.
 
-Be sure that the
-symbols in your equation have been defined before or immediately following
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+\subsection{Data Quality Management}
+Data quality management is a strategic approach aimed at preserving data quality by incorporating activities such as planning, execution, and control to assess and maintain high-quality data standards.
 
-\subsection{\LaTeX-Specific Advice}
+\subsubsection{Components of DQM}
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
+DMBOK identifies critical components of DQM:
+\begin{itemize}
+    \item \textbf{Governance}: Establishing accountability structures for data quality.
+    \item \textbf{Profiling and Cleansing}: Identifying and resolving quality issues.
+    \item \textbf{Root Cause Analysis}: Addressing systemic issues that cause poor data quality.
+    \item \textbf{Monitoring and Improvement}: Continuously assessing and enhancing quality metrics.
+\end{itemize}
 
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
+The DMBOK life cycle comprises six phases: planning, implementation, evaluation, monitoring, maintenance, and improvement. This iterative process ensures data quality aligns with organizational goals.
 
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
+\subsubsection{Challenges in Data Quality Management}
+DMBOK highlights several challenges:
+\begin{itemize}
+    \item \textbf{Data Silos}: Fragmented systems leading to inconsistent data.
+    \item \textbf{Dynamic Data}: Increased volume and complexity in big data ecosystems.
+    \item \textbf{Lack of Standards}: Disparate definitions of data quality across departments.
+    \item \textbf{Human Error}: Manual interventions that introduce inaccuracies.
+\end{itemize}
 
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
+\subsection{Data Quality Maturity}
 
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
+Managing data quality effectively requires aligning data quality practices with organizational activities \cite{loshin_dqi}.
+However, data management is often treated as secondary to functional needs, leading to siloed systems.
+A data quality maturity model, adapted from the Capability Maturity Model (CMM), helps organizations assess and improve their practices, moving from ad hoc processes to optimized systems.
 
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
+\subsection{Data Quality Maturity Model}
 
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
+The maturity model connects organizational data practices to higher levels of performance and quality by addressing key components of data management \cite{loshin_dqi}. 
+% Organizational maturity in managing data quality is reflected in the following components:
 
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
+% \begin{itemize}
+%     \item \textbf{Data Quality Expectations}: Aligns understanding between IT and business to define and use data quality dimensions effectively.
+%     \item \textbf{Policies}: Evolves from informal, undocumented approaches to fully integrated, auditable policies tied to business activities.
+%     \item \textbf{Procedures}: High-performance organizations rely on well-defined processes and protocols to ensure information quality.
+%     \item \textbf{Governance}: Develops through bottom-up information sharing and top-down formalization of responsibilities.
+%     \item \textbf{Standards}: Maturity is reflected in how data standards are defined and implemented to ensure interoperability.
+%     \item \textbf{Technology}: Shifts from tool acquisition to enterprise-wide, service-oriented approaches for data quality improvement.
+%     \item \textbf{Performance Management}: Focuses on defining objectives, measuring conformance, and meeting performance goals.
+% \end{itemize}
 
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A
-minimum of one author is required for all conference articles. Author names
-should be listed starting from left to right and then moving down to the
-next line. This is the author sequence that will be used in future citations
-and by indexing services. Names should not be listed in columns nor group by
-affiliation. Please keep your affiliations as succinct as possible (for
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not
-topically subordinate to each other. Examples include Acknowledgments and
-References and, for these, the correct style to use is ``Heading 5''. Use
-``figure caption'' for your Figure captions, and ``table head'' for your
-table title. Run-in heads, such as ``Abstract'', will require you to apply a
-style (in this case, italic) in addition to the style provided by the drop
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For
-example, the paper title is the primary text head because all subsequent
-material relates and elaborates on this one topic. If there are two or more
-sub-topics, the next level head (uppercase Roman numerals) should be used
-and, conversely, if there are not at least two sub-topics, then no subheads
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
-bottom of columns. Avoid placing them in the middle of columns. Large
-figures and tables may span across both columns. Figure captions should be
-below the figures; table heads should appear above the tables. Insert
-figures and tables after they are cited in the text. Use the abbreviation
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
+% First part of the table
+\begin{table}[H]
+\caption{Comparison of Maturity Models}
+\label{tab:comparison-dqm-part1}
+\centering
+\begin{tabular}{|p{1.5cm}|p{3cm}|p{3cm}|}
 \hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4}
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\textbf{References} & \textbf{Maturity Levels} & \textbf{Dimensions} \\ \hline
+Loshin \cite{loshin_dqi} & Initial, Repeatable, Defined, Managed, Optimized & Data Quality Expectations, Dimensions of Data Quality, Policies, Procedures, Governance, Standards, Technology, Performance Management \\ \hline
+Ryu, K-S et al \cite{ryu2006dqm} & Initial, Defined, Managed, Optimized & Total corporate integration point of view, Data structure quality management point of view, Maturity stages point of view \\ \hline
+Kirikoglu \cite{kirikoglu2017dqm} & Person, dependent and basic, Policies, standards, and procedures, Defined and stable, Managed and standardized, Continues improvement & Disciplined process, Standard consistent process, Predictable process, Continuously improving process \\ \hline
+Ismael, C et al \cite{ismael2003caldea} & Initial, Definition, Integration, Quantitative Management, Optimizing & Data acquisition processes, Data product manufacturing process, and Data maintenance process \\ \hline
 \end{tabular}
-\label{tab1}
-\end{center}
 \end{table}
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
+% % Second part of the table
+% \begin{table}[h!]
+% \caption{Comparison of Maturity Models (Part 2)}
+% \label{tab:comparison-dqm-part2}
+% \centering
+% \begin{tabular}{|p{1.5cm}|p{3cm}|p{3cm}|}
+% \hline
+% \textbf{References} & \textbf{Maturity Levels} & \textbf{Dimensions} \\ \hline
+
+% \end{tabular}
+% \end{table}
+
+In this study, the author selected David Loshin's data quality maturity model.
+This model was chosen because its dimensions are comprehensive and more adaptable for application in various companies, including PT Bank XYZ, compared to other models.
+
+\section{Research Method}
+
+This research stage as shown by figure \ref{fig:research-step} begins with problem identification by asking Director of Operations where the key issue is defined to guide the study.
+Next, a literature review is conducted to previous research on the topic.
+Following this, a research instrument is developed using Data Quality Framework by David Loshin \cite{loshin_dqi} as interview guides.
+After the data is collected, a data quality management maturity assessment is performed.
+Finally, based on the findings, a data quality improvement strategy is developed to enhance the quality and effectiveness of the data for future analysis based on the Data Quality Activities by DMBOK.
+\begin{figure}[H]
+\centerline{\includegraphics[width=0.4\textwidth]{figures/AlurPenelitian.png}}
+\caption{Research Stages}
+\label{fig:research-step}
 \end{figure}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
-rather than symbols or abbreviations when writing Figure axis labels to
-avoid confusing the reader. As an example, write the quantity
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
-units in the label, present them within parentheses. Do not label axes only
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
-quantities and units. For example, write ``Temperature (K)'', not
-``Temperature/K''.
+\subsection{Research Instruments}
 
-\section*{Acknowledgment}
+In this study, the DQM maturity level characteristic matrix, derived from David Loshin’s Data Quality Framework (DQF) \cite{loshin_dqi} is used as the instrument.
+The matrix consists of a checklist containing 121 characteristics spread across 8 components defined in the DQF, as summarized in TABLE \ref{tab:questionnare-areas}.
+\begin{table}[H]
+\caption{Table of Questionnaire Areas and Number of Questions}
+\label{tab:questionnare-areas}
+\centering
+\begin{tabular}{|l|c|}
+\hline
+\textbf{Questionnaire Area} & \textbf{\#Question} \\
+\hline
+Data Quality Expectations & 18 \\
+\hline
+Data Quality Dimensions & 14 \\
+\hline
+Information Policies & 17 \\
+\hline
+Data Quality Protocols & 20 \\
+\hline
+Data Governance & 18 \\
+\hline
+Data Standards & 20 \\
+\hline
+Data Quality Technology & 12 \\
+\hline
+Performance Management & 14 \\
+\hline
+\textbf{Total} & \textbf{133} \\
+\hline
+\end{tabular}
+\end{table}
 
-The preferred spelling of the word ``acknowledgment'' in America is without
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
-acknowledgments in the unnumbered footnote on the first page.
+\subsection{Data Collection}
+Data was collected through interviews with two Subject Matter Experts (SME) in the organization, Head of Information Technology (IT) and Head of Operations.
+The interviews included a set of pre-planned questions using the research instrument to understand how the organization manages data quality.
+Interviews were conducted in person or online to accommodate participants’ schedules.
+The responses were recorded and transcribed for analysis.
 
-\section*{References}
+\subsection{Data Analysis Techniques for Assessing Data Quality Maturity Levels}
+This research used a mixed-methods approach for data analysis combining both qualitative and quantitative methods.
+Data was collected through interviews using preplanned questions.
+The interviews were transcribed for analysis and the transcripts were reviewed to evaluate the characteristics of each component in the DQF.
+\cite{loshin_dqi}.
+Each characteristic was assessed and given a score 1 if it was true and 0 if it was not.
+The scores for each level within a component were averaged and summed to find the overall quality of the component.
+The overall data quality maturity level was then calculated by averaging the maturity levels of each component.
 
-Please number citations consecutively within brackets \cite{b1}. The
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+\subsection{Data Quality Improvement Strategy}
+The characteristics that the organization has not fully met are identified.
+These characteristics are marked by a score of 0 in the evaluation.
+They highlight areas where the organization’s data quality management practices need improvement.
+These characteristics are mapped to the Data Quality Management (DQM) activities in the DMBOK \cite{DAMA_2013}.
+This mapping helps align the organization’s practices with established best practices.
+From this, the analysis provides specific recommendations and strategies to improve data quality management.
 
-Number footnotes separately in superscripts. Place the actual footnote at
-the bottom of the column in which it was cited. Do not put footnotes in the
-abstract or reference list. Use letters for table footnotes.
+\section{Result and Discussions}
+\subsection{Assessment Result}
+The results indicated that three areas met the initial level, four areas were at the repeatable level, and one reached the defined level.
+As a result, the overall average maturity level was 2.04.
+Table \ref{tab:maturity-level} provides more details on the expected level for each area.
 
-Unless there are six authors or more give all authors' names; do not use
-``et al.''. Papers that have not been published, even if they have been
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
-that have been accepted for publication should be cited as ``in press'' \cite{b5}.
-Capitalize only the first word in a paper title, except for proper nouns and
-element symbols.
+\begin{table}[H]
+\caption{Maturity Level}
+\label{tab:maturity-level}
+\centering
+\begin{tabular}{|p{0.3cm}|p{3cm}|p{1cm}|p{2cm}|}
+\hline
+\textbf{No} & \textbf{Questionnaire Area} & \textbf{Maturity Level}&\textbf{Level Description} \\
+\hline
+1 & Data Quality Expectations & 2.08 & Repeatable\\
+\hline
+2 & Data Quality Dimensions & 2.00 & Repeatable\\
+\hline
+3 & Information Policies & 1.90 & Initial\\
+\hline
+4 & Data Quality Protocols & 2.33 & Repeatable \\
+\hline
+5 & Data Governance & 1.33 & Initial \\
+\hline
+6 & Data Standards & 3.00 & Managed \\
+\hline
+7 & Data Quality Technology & 1.58 & Initial\\
+\hline
+8 & Performance Management & 2.08 & Repeatable\\
+\hline
+\multicolumn{2}{|l|}{\textbf{Average}} & \textbf{2.04}& \textbf{Repeatable} \\
+\hline
+\end{tabular}
+\end{table}
 
-For papers published in translation journals, please give the English
-citation first, followed by the original foreign-language citation \cite{b6}.
+Based on the interviews, the current condition of each data quality component in the company is as follows.
+\begin{itemize}
+\item \textbf{Data Quality Expectations}: This organization lacks internal documents outlining data quality expectations and relies only on related regulations like Peraturan Otoritas Jasa Keuangan (POJK) and Surat Edaran Otoritas Jasa Keuangan (SEOJK).
+There are no clear expectations or documentation for data quality dimensions.
+\item \textbf{Data Quality Dimensions}: The company has no formal definition of data quality or clear categories for measuring it.
+There are no rules or reports for data quality, and no connection between data quality and business impacts.
+There is no data quality matrix, SLA document, or monitoring of SLA.
+\item \textbf{Information Policy}: The company has no formal data quality policy or guidelines for handling data issues.
+The existing SLA between Pusintek and Biro SDM does not address data quality, and there is no automated system for data quality governance.
+\item \textbf{Data Quality Protocols}:The company has identified some causes of data quality issues, but errors keep repeating.
+Root cause analysis is done case by case without using data quality or validation rules.
+There is no procedure to check data accuracy or validity.
+There is also no process for handling incomplete or incorrect data.
+\item \textbf{Data Governance}: The company does not have a dedicated data steward, and data management responsibilities are handled by the IT division.
+There is no team or manager for data repairs, and no group exists to design or recommend data governance programs and policies.
+There are also no guiding principles or data governance policies in place.
+\item \textbf{Data Standards}: There are no defined data elements to identify information, and no certification activities for trusted or owned data sources.
+Metadata standards are still controlled by IT and there is no process to manage data exchange standards.
+Also, there is no board to oversee and maintain internal and external data standards.
+\item \textbf{Data Quality Technology}: The company lacks tools to objectively measure data quality, find or connect data, and there is no standard procedure for using data quality technology to assess or improve it.
+Additionally, validation processes based on business rules have not been implemented.
+\item \textbf{Performance Management}: The company does not use data profiling to identify errors, lacks a framework to analyze the impact of data quality, and has no defined data quality service components to detect errors early in the process.
+\end{itemize}
 
-\section*{References}
+A good practice in data quality management is to set the target maturity level one level above the current state.
+Although organizations might want to reach the highest level of maturity, the challenges they face and the advisory role of data quality managers often make this difficult.
+Instead, it is better to reach for a level that meets the organization's goals while still being achievable within the team’s capabilities \cite{loshin_dqi}.
+Figure \ref{fig:maturity-level-spider-graph} shows the assessment result of PT Bank XYZ
+
+\begin{figure}[h]
+    \centering
+    \begin{tikzpicture}[scale=0.3]
+        % Define the origin of the spider graph
+        \coordinate (origin) at (0, 0);
+
+        % Define the maturity levels and corresponding labels
+        \foreach[count=\i] \radius/\label in {
+            2.08/Data Quality \\ Expectations,
+            2.00/Data Quality \\ Dimensions,
+            1.90/Information \\ Policies,
+            2.33/Data Quality \\ Protocols,
+            1.33/Data \\ Governance,
+            3.00/Data \\ Standards,
+            1.58/Data Quality \\ Technology,
+            2.08/Performance \\ Management}{
+            \coordinate (\i) at (\i * 360 / 8: \radius * 3); % Scale radius by 3 for better visibility
+            \node[align=center] (label) at (\i * 360 / 8: 11) {\normalsize\label}; % Place labels
+            \draw[gray, dotted] (origin) -- (label); % Connect labels to the origin
+        }
+
+        % Draw the filled polygon connecting all points
+        \draw [fill=blue!20, opacity=.7] (1)
+                                    \foreach \i in {2,...,8}{-- (\i)} -- cycle;
+
+        % Add the grid lines for reference
+        \foreach \r in {1, 2, 3} {
+            \draw [gray, dotted] (0, 0) circle (\r * 3);
+        }
+
+        % Add concentric circle labels
+        % \node at (0, 0) {\footnotesize\textbf{0}};
+        \node at (112.5:3) {\footnotesize\textbf{1}};
+        \node at (112.5:6) {\footnotesize\textbf{2}};
+        \node at (112.5:9) {\footnotesize\textbf{3}};
+    \end{tikzpicture}
+    \caption{Maturity Level Spider Graph}
+    \label{fig:maturity-level-spider-graph}
+\end{figure}
+
+By targeting a level just above the current one, organizations can make gradual improvements without overwhelming the staff.
+This approach helps achieve data quality benefits step by step, with clear goals along the way.
+In the end, this method leads to more manageable and effective improvements in data quality \cite{loshin_dqi}.
+
+\subsection{Recommendations}
+Gaps between the company current data quality and the target expectations through assessments or interviews is identified.
+These gaps show characteristics that are not yet implemented.
+Based on these gaps, recommendations are made to improve DQM using DQM activities from the DMBOK to reach one level above the current state.
+The complete gap analysis to gap analysis can be seen in Table \ref{tab:mapping}.
+The activities to improve Data Quality Management (DQM) based on the mapping to the Data Management Body of Knowledge (DMBOK) are listed below:
+\begin{enumerate}
+    \item Manage Data Quality Rules (DQM Activity 7.1) \\ Managing data quality rules means analyzing data to create rules, adding rules to system processes, and documenting them clearly.
+The rules should support business goals, be checked through data analysis, and confirmed by experts.
+They should also be available to all data users for better understanding and feedback.
+Below is a list of characteristics the company has not yet implemented, based on component maturity description of data quality management by David Loshin \cite{loshin_dqi}.
+        \begin{itemize}
+            \item "No data quality expectations have been documented"
+            \item "Expectations associated with dimensions of data quality associated with data values, formats, and semantics can be articulated using data quality rules
+            \item "Policies are informal"
+            \item 
+        \end{itemize}
+\end{enumerate}
+
+\begin{table*}[h]
+\caption{Mapping the gaps in DQM maturity levels to the activities outlined in DQM-DMBOK}
+\label{tab:mapping}
+\centering
+\begin{tabular}{|p{2cm}|p{5cm}|p{5cm}|p{2cm}|}
+\hline
+\textbf{Data Quality Component} & \textbf{Characteristics} & \textbf{Recommendations} & \textbf{DMBOK Activity} \\
+\hline
+Data Quality Expectations (target = 3) & "No data quality expectations have been documented", "Expectations associated with dimensions of data quality associated with data values, formats, and semantics can be articulated using data quality rules" & The company should consider create internal documents for data quality expectations, consistently document rules, define them by quality aspects, and connect them to business impact for better results.
+The company should include expectations and guidelines for data quality dimensions, such as data values, to help clearly define what is being measured and improve consistency in measurement and issue management & 7.1 \\
+
+\hline
+Data Quality Dimensions (target = 3) & "Recognition of common dimensions for measuring quality of data values", "Basic reporting for simple data quality measurements" & It is recommended that the company define data quality and establish common dimensions for measuring data values.
+This will help track data quality, inform users, and manage risks from changes.
+The company should create reports on data quality, including a scorecard, trends, SLA metrics, and issue tracking, to show progress and the impact of improvements.
+& 7.2, 7.5 \\
+\hline
+Information Policies (target = 2) & "Policies are informal", "Policies are undocumented", "Initial policies defined for reacting to data issues" & The company is encouraged to create a formal data quality policy, document clear data quality rules, and integrate them into system development.
+This will set expectations, ensure control, and support ongoing measurement and reporting & 7.1 \\
+\hline
+% Information Policies (target = 2) & " Initial policies defined for reacting to data issues" & There is no policy for handling data issues & 7.1 \\
+% \hline
+Data Quality Protocols (target = 3) &
+% "Failures reacted to reactively, with no coordination with business processes."
+"Root causes unidentified, errors repeated", 
+"Errors tracked for incompleteness and invalid syntax", 
+"Basic root cause analysis via data quality rules"
+& 
+There is a need for data controls to be deployed across the enterprise, participants to publish data quality measurements, and data quality management practices to be transparent.
+& 7.4\\
+\hline
+Data Governance (target = 2)& 
+"Informal communication about data quality between IT and other divisions", 
+% "IT support handles most data quality issues without a formal strategy."
+"No dedicated data stewardship; responsibilities are ad hoc", 
+"Best practices for data quality are shared informally"
+% "No formal workgroup for data governance or guiding principles in development."
+&
+There is a need to formalize Data Stewardship roles and responsibilities, develop and document guiding principles, data quality charter, and policies, establish a formal data governance workgroup with key stakeholders.
+& 7.5 \\
+\hline
+Data Standards (target = 4) & 
+"Certification process for trusted data sources is still not defined", 
+% "Master data reference sets have been identified and are managed, but further formalization is needed."
+"No formal process for overseeing the management of exchange standards", 
+"No Data Standards Oversight Board exists"
+& 
+There is a need to implement a Master Data Management (MDM) solution to formalize master data concepts and develop a clear taxonomy for data standards, ensuring it is endorsed and widely adopted.
+& 7.3 \\
+\hline
+Data Quality Technology (target = 2) & 
+"Tools for assessing objective data quality not available", 
+"Data parsing, standardization, and cleansing available", 
+"Data quality technology for matching and linking not available"
+& 
+There is a need to implement tools for assessing data quality, establish technology for data matching, define standardized procedures for quality assessment, and use business rule-based validation techniques.
+% "Standardize technology components for data validation, certification, assurance, and reporting across the organization."
+% "Ensure technology components are standardized at both the service and implementation layers."
+& 7.2 \\
+
+\hline
+Performance Management (target = 3) & "Data profiling used to identify data failures in process" & It is advisable for the company to implement data profiling to identify errors, set clear data quality expectations, establish system controls, and support ongoing measurement and reporting.
+& 7.1 \\
+\hline
+\multicolumn{2}{|l|}{\textbf{Average}} & \textbf{2.04} & \textbf{Repeatable} \\
+\hline
+\end{tabular}
+\end{table*}
+
+\section{Conclusions and Future Works}
+
+\subsection{Conclusions}
+
+The study's findings lead to the following conclusions:
+
+\begin{enumerate}
+    \item The results of measuring the maturity level at PT Bank XYZ using the Loshin and DMBOK method \cite{loshin_dqi}\cite{DAMA_2013} indicate that the organization is still at level two(Repeatable).
+Our study shows that PT Bank XYZ has good level of Data Standard but is lacking in other areas such as Data Quality Technology and Data Governance.
+    \item PT Bank XYZ has demonstrated a varying level of maturity across different data management domains.
+While the organization excels in data standards, achieving a maturity level of 3.00 (Managed), there is still significant room for improvement in areas such as Data Governance (1.33, Initial), Information Policies (1.90, Initial), and Data Quality Technology (1.58, Initial).
+The maturity levels for Data Quality Expectations, Data Quality Dimensions, and Data Quality Protocols fall within the Repeatable stage, indicating a developing but inconsistent approach.
+To advance towards higher maturity, the bank should focus on formalizing data governance structures, improving technological support for data quality, and establishing clearer policies and protocols for managing data.
+    \item The Loshin Data Quality Management (DQM) framework helps assess an organization's data quality practices and maturity.
+It identifies gaps across key dimensions like governance, technology, and performance management, offering actionable recommendations for improvement.
+PT Bank XYZ can use this framework to enhance data management, strengthen governance, and ensure more reliable data.
+\end{enumerate}
+
+\subsection{Limitations and Future works}
+
+The author hopes that this research can benefit PT Bank XYZ.
+Based on the recommendations from the research results, PT Bank XYZ can plan and prepare to implement the given recommendations.
+Thus, it is expected that data quality management at PT Bank XYZ can be implemented and improved, leading to better data quality.
+The author also hopes this research will be useful for future studies.
+The following are the author's suggestions for future research:
+\begin{enumerate}
+    \item Further evaluation can be conducted using the same method. It is within a organization's interest to reach a higher data quality management maturity level.
+    \item Maturity measurement must be carried out continuously to reach the final level.
+\end{enumerate}
+
+\section*{ACKNOWLEDGMENT}
+
+Hopefully this research will provide value and benefit to readers, despite any shortcomings in its writing.
+The author extends gratitude to everyone who has offered support and assistance in completing this paper.
+
+\section*{Work Division}
+\begin{itemize}
+    \item Samuel: Data collection, Conducting Interview, Abstract, Introduction, topic, Process the data using Excel
+    \item Jon: Literature Study, State of the art, Result Discussion, Conclusion (Assessment Result, Gap Analysis), \LaTeX{} Formatting
+    \item Filza: Research Method, Result and Discussion (Assessment Result, Gap Analysis)
+\end{itemize}
+
+% \section*{References}
 \bibliographystyle{IEEEtran}

### 2024-12-26 paper.tex
Changes from papeeria

@@
 \section{Introduction}
+% Organizations today generate and manage data from a variety of sources, requiring robust systems to handle customer profiles, financial transactions, account management, and credit applications.
+Managing data quality (DQM) has become a critical focus for organizations, particularly in the banking sector, where accurate and reliable data serves as a cornerstone for operational efficiency and strategic growth.
+Poor data quality can lead to inaccuracies that hinder decision-making, such as selecting optimal business locations, and can expose organizations to reputational and financial risks.
+
+% In the context of PT Bank XYZ, understanding the maturity level of Data Quality Management (DQM) is crucial to identify gaps and opportunities for improvement.
+The bank operates in a complex data ecosystem, integrating Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and regulatory compliance tools.
+These systems demand high data quality to meet operational needs and comply with regulations, such as POJK No.
+8/2023 on Anti-Money Laundering and Counter Terrorism Financing.
+
+% To address these challenges, this paper explores the data quality maturity level of data quality management at PT XYZ and outlines strategies to enhance its governance framework.
+The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands.
+
+% The study is guided by the following research questions:
+% \begin{enumerate}
+%     \item What is the current maturity level of data quality management at PT XYZ?
+%     \item How can PT XYZ improve its data quality management practices to address regulatory, operational, and strategic risks?
+% \end{enumerate}
+
 Organizations today generate and manage data from a variety of sources, requiring robust systems to handle customer profiles, financial transactions, account management, and credit applications.
@@
 
-In the context of PT Bank XYZ, understanding the maturity level of Data Quality Management (DQM) is crucial to identify gaps and opportunities for improvement.
-The bank operates in a complex data ecosystem, integrating Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and regulatory compliance tools.
-These systems demand high data quality to meet operational needs and comply with regulations, such as POJK No.
-8/2023 on Anti-Money Laundering and Counter Terrorism Financing.
+PT Bank XYZ, a microfinance-focused bank headquartered in Kabupaten Bandung Barat, operates a network of 24 branches and one cash office across Java, serving diverse customer needs through products like savings, deposits, and credit.
+As of October 2024, the bank manages assets of Rp 366 billion and employs approximately 300 staff, including an Information Technology (IT) division responsible for supporting business data analysis, regulatory reporting, and information systems.
+Despite its growth, the bank faces significant challenges, including fragmented data sources, increasing demands for internal and external data reporting, and frequent penalties from regulators such as OJK due to reporting errors.
+Additionally, regulatory requirements like POJK No.
+8/2023 on Anti-Money Laundering and Counter-Terrorism Financing underscore the importance of accurate and up-to-date data management practices.
 
-To address these challenges, this paper explores the data quality maturity level of data quality management at PT XYZ and outlines strategies to enhance its governance framework.
+In the context of these challenges, understanding the maturity level of DQM at PT Bank XYZ is critical to identifying gaps and uncovering opportunities for improvement.
+The bank operates in a complex data ecosystem that integrates Core Banking Systems (CBS), Customer Relationship Management (CRM) platforms, and Loan Origination Systems (LOS), among others, without mechanisms for aggregating or monitoring data quality.
+As the organization strives to improve digital services and ensure compliance with evolving regulatory standards, addressing the risks of poor data quality—such as reputational damage, reporting errors, financial losses, and strategic missteps—becomes essential.
+
+To address these challenges, this paper explores the maturity level of data quality management at PT Bank XYZ and outlines strategies to enhance its governance framework.
 The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands.
-
-The study is guided by the following research questions:
-\begin{enumerate}
-    \item What is the current maturity level of data quality management at PT XYZ?
-    \item How can PT XYZ improve its data quality management practices to address regulatory, operational, and strategic risks?
-\end{enumerate}
+This study is structured around two primary research questions: First, it seeks to determine the current maturity level of data quality management (DQM) at PT Bank XYZ.
+Second, it aims to explore strategies for improving the bank’s DQM practices to address regulatory, operational, and strategic risks effectively.
 

### 2024-12-26 paper.tex
Changes from papeeria

@@
 This study evaluates the DQM maturity at PT Bank XYZ using David Loshin’s Data Quality Framework and the Data Management Body of Knowledge (DMBOK) guidelines.
+
 The research involves comprehensive interviews with key stakeholders to assess the bank's performance across eight DQM components, including governance, standards, and technology.
@@
 These gaps hinder the bank’s ability to fully leverage its data assets for strategic growth and regulatory compliance.
+
 To address these challenges, the study provides actionable recommendations aimed at enhancing DQM practices.
@@
 The study emphasizes the need for a holistic approach to data integration, quality monitoring, and regulatory compliance to ensure sustainable growth and resilience in the face of increasing data demands.
-This study is structured around two primary research questions: First, it seeks to determine the current maturity level of data quality management (DQM) at PT Bank XYZ.
-Second, it aims to explore strategies for improving the bank’s DQM practices to address regulatory, operational, and strategic risks effectively.
+The objective of this study is to improve and evaluate the data quality management processes at PT Bank XYZ.
 
@@
     \item \textbf{Timeliness}: Evaluates whether the data is up-to-date and relevant at the time of use, crucial for dynamic and real-time decision-making \cite{mashoufi2023data}.
-    \item \textbf{Validity}: Verifies that the data adheres to predefined formats, business rules, and constraints \cite{mcgilvray2021executing}.
     \item \textbf{Accuracy}: Measures whether the data accurately represents real-world values or concepts, ensuring trustworthiness \cite{west2021towards}.
@@
 
-\section{Research Method}
+% \section{Research Method}
 
-This research stage as shown by figure \ref{fig:research-step} begins with problem identification by asking Director of Operations where the key issue is defined to guide the study.
+% This research stage as shown by figure \ref{fig:research-step} begins with problem identification by asking Director of Operations where the key issue is defined to guide the study.
 Next, a literature review is conducted to previous research on the topic.
@@
 Finally, based on the findings, a data quality improvement strategy is developed to enhance the quality and effectiveness of the data for future analysis based on the Data Quality Activities by DMBOK.
-\begin{figure}[H]
-\centerline{\includegraphics[width=0.4\textwidth]{figures/AlurPenelitian.png}}
+% \begin{figure}[H]
+% \centerline{\includegraphics[width=0.4\textwidth]{figures/AlurPenelitian.png}}
+% \caption{Research Stages}
+% \label{fig:research-step}
+% \end{figure}
+
+% \subsection{Research Instruments}
+
+% In this study, the DQM maturity level characteristic matrix, derived from David Loshin’s Data Quality Framework (DQF) \cite{loshin_dqi} is used as the instrument.
+The matrix consists of a checklist containing 121 characteristics spread across 8 components defined in the DQF, as summarized in TABLE \ref{tab:questionnare-areas}.
+% \begin{table}[H]
+% \caption{Table of Questionnaire Areas and Number of Questions}
+% \label{tab:questionnare-areas}
+% \centering
+% \begin{tabular}{|l|c|}
+% \hline
+% \textbf{Questionnaire Area} & \textbf{\#Question} \\
+% \hline
+% Data Quality Expectations & 18 \\
+% \hline
+% Data Quality Dimensions & 14 \\
+% \hline
+% Information Policies & 17 \\
+% \hline
+% Data Quality Protocols & 20 \\
+% \hline
+% Data Governance & 18 \\
+% \hline
+% Data Standards & 20 \\
+% \hline
+% Data Quality Technology & 12 \\
+% \hline
+% Performance Management & 14 \\
+% \hline
+% \textbf{Total} & \textbf{133} \\
+% \hline
+% \end{tabular}
+% \end{table}
+
+% \subsection{Data Collection}
+% Data was collected through interviews with two Subject Matter Experts (SME) in the organization, Head of Information Technology (IT) and Head of Operations.
+The interviews included a set of pre-planned questions using the research instrument to understand how the organization manages data quality.
+Interviews were conducted in person or online to accommodate participants’ schedules.
+The responses were recorded and transcribed for analysis.
+
+% \subsection{Data Analysis Techniques for Assessing Data Quality Maturity Levels}
+% This research used a mixed-methods approach for data analysis combining both qualitative and quantitative methods.
+Data was collected through interviews using preplanned questions.
+The interviews were transcribed for analysis and the transcripts were reviewed to evaluate the characteristics of each component in the DQF.
+\cite{loshin_dqi}.
+% Each characteristic was assessed and given a score 1 if it was true and 0 if it was not.
+The scores for each level within a component were averaged and summed to find the overall quality of the component.
+The overall data quality maturity level was then calculated by averaging the maturity levels of each component.
+
+% \subsection{Data Quality Improvement Strategy}
+% The characteristics that the organization has not fully met are identified.
+These characteristics are marked by a score of 0 in the evaluation.
+They highlight areas where the organization’s data quality management practices need improvement.
+These characteristics are mapped to the Data Quality Management (DQM) activities in the DMBOK \cite{DAMA_2013}.
+This mapping helps align the organization’s practices with established best practices.
+From this, the analysis provides specific recommendations and strategies to improve data quality management.
+
+\section{Research Methodology}
+
+This study adopts a structured approach to evaluate and improve the data quality management (DQM) maturity level at PT Bank XYZ.
+The methodology integrates qualitative and quantitative methods, using David Loshin’s Data Quality Framework (DQF) and the Data Management Body of Knowledge (DMBOK) as guiding models.
+Figure \ref{fig:research-stages} provides an overview of the research stages, while the subsequent subsections outline the specific methods employed.
+
+\subsection{Research Stages}
+
+The research process consists of the following stages (illustrated in Fig. \ref{fig:research-stages}):
+\begin{itemize}
+    \item \textbf{Problem Identification:} Discussions with the Director of Operations were conducted to pinpoint key organizational challenges related to data quality management.
+    \item \textbf{Literature Review:} Relevant studies and frameworks on DQM and maturity assessment were reviewed to establish a theoretical foundation.
+    \item \textbf{Research Instrument Development:} A customized checklist was designed using Loshin’s DQM framework to assess maturity across eight components.
+    \item \textbf{Data Collection:} Qualitative data was gathered through stakeholder interviews, targeting subject matter experts (SMEs) within the organization.
+    \item \textbf{Data Analysis and Assessment:} The collected data was evaluated to calculate the organization’s DQM maturity level.
+    \item \textbf{Strategy Development:} Recommendations were proposed based on the gaps identified in the maturity assessment, aligning with DMBOK best practices.
+\end{itemize}
+
+\begin{figure}[h]
+\centerline{\includegraphics[width=0.45\textwidth]{figures/AlurPenelitian.png}}
 \caption{Research Stages}
-\label{fig:research-step}
+\label{fig:research-stages}
 \end{figure}
 
-\subsection{Research Instruments}
+\subsection{Research Instrument}
 
-In this study, the DQM maturity level characteristic matrix, derived from David Loshin’s Data Quality Framework (DQF) \cite{loshin_dqi} is used as the instrument.
-The matrix consists of a checklist containing 121 characteristics spread across 8 components defined in the DQF, as summarized in TABLE \ref{tab:questionnare-areas}.
-\begin{table}[H]
-\caption{Table of Questionnaire Areas and Number of Questions}
-\label{tab:questionnare-areas}
+The primary tool for data collection was the DQM Maturity Level Characteristic Matrix, derived from David Loshin’s DQM Framework \cite{loshin_dqi}.
+The matrix includes a checklist of 133 characteristics across eight DQM components, as summarized in Table \ref{tab:questionnaire}.
+These components cover key areas such as governance, standards, and performance management, ensuring a comprehensive evaluation of the organization’s data quality practices.
+
+\begin{table}[h]
+\caption{Questionnaire Areas and Number of Questions}
+\label{tab:questionnaire}
 \centering
@@
 \hline
-\textbf{Questionnaire Area} & \textbf{\#Question} \\
+\textbf{Questionnaire Area} & \textbf{Number of Questions} \\
 \hline
 Data Quality Expectations & 18 \\
-\hline
 Data Quality Dimensions & 14 \\
-\hline
 Information Policies & 17 \\
-\hline
 Data Quality Protocols & 20 \\
-\hline
 Data Governance & 18 \\
-\hline
 Data Standards & 20 \\
-\hline
 Data Quality Technology & 12 \\
-\hline
 Performance Management & 14 \\
@@
 \subsection{Data Collection}
-Data was collected through interviews with two Subject Matter Experts (SME) in the organization, Head of Information Technology (IT) and Head of Operations.
-The interviews included a set of pre-planned questions using the research instrument to understand how the organization manages data quality.
-Interviews were conducted in person or online to accommodate participants’ schedules.
-The responses were recorded and transcribed for analysis.
 
-\subsection{Data Analysis Techniques for Assessing Data Quality Maturity Levels}
-This research used a mixed-methods approach for data analysis combining both qualitative and quantitative methods.
-Data was collected through interviews using preplanned questions.
-The interviews were transcribed for analysis and the transcripts were reviewed to evaluate the characteristics of each component in the DQF.
-\cite{loshin_dqi}.
-Each characteristic was assessed and given a score 1 if it was true and 0 if it was not.
-The scores for each level within a component were averaged and summed to find the overall quality of the component.
-The overall data quality maturity level was then calculated by averaging the maturity levels of each component.
+Data collection focused on qualitative insights gathered through structured interviews with two Subject Matter Experts (SMEs): the Head of Information Technology (IT) and the Head of Operations.
+The interviews were guided by pre-designed questions derived from the DQM checklist to explore organizational practices in data management.
+Interviews were conducted both in-person and virtually, ensuring flexibility in scheduling.
+All responses were recorded, transcribed, and organized for subsequent analysis.
 
-\subsection{Data Quality Improvement Strategy}
-The characteristics that the organization has not fully met are identified.
-These characteristics are marked by a score of 0 in the evaluation.
-They highlight areas where the organization’s data quality management practices need improvement.
-These characteristics are mapped to the Data Quality Management (DQM) activities in the DMBOK \cite{DAMA_2013}.
-This mapping helps align the organization’s practices with established best practices.
-From this, the analysis provides specific recommendations and strategies to improve data quality management.
+Although interviews were the primary method, incorporating surveys or benchmarking against similar organizations could have added more comparative insights.
+Future studies should consider these additional methods to enhance robustness.
+
+\subsection{Data Analysis}
+
+A structured scoring rubric was used to evaluate the collected data.
+
+\begin{itemize}
+    \item \textbf{Scoring Mechanism:} Each characteristic in the DQM framework was evaluated and assigned a score:
+    \begin{itemize}
+        \item \textbf{1:} If the characteristic was fully met.
+        \item \textbf{0:} If the characteristic was not met.
+    \end{itemize}
+    \item \textbf{Component-Level Averages:} Scores within each DQM component were averaged to compute a maturity level for that component.
+    \item \textbf{Overall Maturity Level:} An overall maturity score was calculated by averaging the maturity levels across all components.
+\end{itemize}
+
+\subsection{Development of Improvement Strategy}
+
+The analysis identified specific characteristics that were not met (scored 0), highlighting gaps in the organization’s DQM practices.
+These gaps were mapped to actionable strategies based on \cite{loshin_dqi} data quality management maturity model.
+For each gap, tailored recommendations were proposed to improve data governance, technology, and overall maturity.
+
+To ensure the feasibility and sustainability of improvements, the strategy targets achieving one maturity level above the organization’s current level \cite{loshin_dqi}.
+While organizations may aspire to reach the highest levels of maturity, attempting to make such a significant leap can overwhelm resources and disrupt ongoing processes.
+A gradual approach, focusing on advancing one level at a time, is more practical and aligns with the organization’s operational capacity.
+This incremental improvement allows PT Bank XYZ to consolidate its gains at each stage, ensuring that new processes, policies, and technologies are effectively integrated before pursuing further advancements.
 
@@
 
-A good practice in data quality management is to set the target maturity level one level above the current state.
+A good practice in data quality management is to set the target maturity level one level above the current state as shown in Table \ref{tab:target-maturity-level}.
 Although organizations might want to reach the highest level of maturity, the challenges they face and the advisory role of data quality managers often make this difficult.
@@
 
-\begin{figure}[h]
+\begin{table}[H]
+\caption{Target Maturity Level}
+\label{tab:target-maturity-level}
 \centering
-    \begin{tikzpicture}[scale=0.3]
+\begin{tabular}{|p{0.3cm}|p{3cm}|p{1cm}|p{2cm}|}
+\hline
+\textbf{No} & \textbf{Questionnaire Area} & \textbf{Target Maturity Level}&\textbf{Level Description} \\
+\hline
+1 & Data Quality Expectations & 3 & Defined\\
+\hline
+2 & Data Quality Dimensions & 3 & Defined\\
+\hline
+3 & Information Policies & 2 & Repeatable\\
+\hline
+4 & Data Quality Protocols & 3 & Defined \\
+\hline
+5 & Data Governance & 2 & Repeatable \\
+\hline
+6 & Data Standards & 4 & Managed \\
+\hline
+7 & Data Quality Technology & 2 & Repeatable\\
+\hline
+8 & Performance Management & 3 & Defined\\
+\hline
+\end{tabular}
+\end{table}
+
+By targeting a level just above the current one, organizations can make gradual improvements without overwhelming the staff.
+This approach helps achieve data quality benefits step by step, with clear goals along the way.
+In the end, this method leads to more manageable and effective improvements in data quality \cite{loshin_dqi}.
+
+% \begin{figure}[H]
+%     \centering
+%     \begin{tikzpicture}[scale=0.3]
+%         % Define the origin of the spider graph
+%         \coordinate (origin) at (0, 0);
+
+%         % Define the maturity levels and corresponding labels
+%         \foreach[count=\i] \radius/\label in {
+%             2.08/Data Quality \\ Expectations,
+%             2.00/Data Quality \\ Dimensions,
+%             1.90/Information \\ Policies,
+%             2.33/Data Quality \\ Protocols,
+%             1.33/Data \\ Governance,
+%             3.00/Data \\ Standards,
+%             1.58/Data Quality \\ Technology,
+%             2.08/Performance \\ Management}{
+%             \coordinate (\i) at (\i * 360 / 8: \radius * 3); % Scale radius by 3 for better visibility
+%             \node[align=center] (label) at (\i * 360 / 8: 11) {\normalsize\label}; % Place labels
+%             \draw[gray, dotted] (origin) -- (label); % Connect labels to the origin
+%         }
+
+%         % Draw the filled polygon connecting all points
+%         \draw [fill=blue!20, opacity=.7] (1)
+%                                     \foreach \i in {2,...,8}{-- (\i)} -- cycle;
+
+%         % Add the grid lines for reference
+%         \foreach \r in {1, 2, 3} {
+%             \draw [gray, dotted] (0, 0) circle (\r * 3);
+%         }
+
+%         % Add concentric circle labels
+%         % \node at (0, 0) {\footnotesize\textbf{0}};
+%         \node at (112.5:3) {\footnotesize\textbf{1}};
+%         \node at (112.5:6) {\footnotesize\textbf{2}};
+%         \node at (112.5:9) {\footnotesize\textbf{3}};
+%     \end{tikzpicture}
+%     \caption{Maturity Level Spider Graph}
+%     \label{fig:maturity-level-spider-graph}
+% \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{tikzpicture}[scale=0.2]
         % Define the origin of the spider graph
@@
 
-        % Define the maturity levels and corresponding labels
+        % Define the actual maturity levels and corresponding labels
         \foreach[count=\i] \radius/\label in {
@@
             2.08/Performance \\ Management}{
-            \coordinate (\i) at (\i * 360 / 8: \radius * 3); % Scale radius by 3 for better visibility
-            \node[align=center] (label) at (\i * 360 / 8: 11) {\normalsize\label}; % Place labels
+            \coordinate (actual-\i) at (\i * 360 / 8: \radius * 3); % Scale radius by 3 for better visibility
+            \node[align=center] (label) at (\i * 360 / 8: 15) {\normalsize\label}; % Place labels at level 5
             \draw[gray, dotted] (origin) -- (label); % Connect labels to the origin
@@
 
-        % Draw the filled polygon connecting all points
-        \draw [fill=blue!20, opacity=.7] (1)
-                                    \foreach \i in {2,...,8}{-- (\i)} -- cycle;
+        % Define the target maturity levels
+        \foreach[count=\i] \radius in {
+            3, % Data Quality Expectations
+            3, % Data Quality Dimensions
+            2, % Information Policies
+            3, % Data Quality Protocols
+            2, % Data Governance
+            4, % Data Standards
+            2, % Data Quality Technology
+            3  % Performance Management
+        }{
+            \coordinate (target-\i) at (\i * 360 / 8: \radius * 3); % Scale radius by 3 for better visibility
+        }
+
+        % Draw the actual maturity level polygon
+        \draw [fill=blue!20, opacity=.7] (actual-1)
+                                    \foreach \i in {2,...,8}{-- (actual-\i)} -- cycle;
+
+        % Draw the target maturity level polygon
+        \draw [red, thick, dashed] (target-1)
+                                    \foreach \i in {2,...,8}{-- (target-\i)} -- cycle;
 
         % Add the grid lines for reference
-        \foreach \r in {1, 2, 3} {
+        \foreach \r in {1, 2, 3, 4, 5} {
             \draw [gray, dotted] (0, 0) circle (\r * 3);
@@
         % Add concentric circle labels
-        % \node at (0, 0) {\footnotesize\textbf{0}};
         \node at (112.5:3) {\footnotesize\textbf{1}};
@@
         \node at (112.5:9) {\footnotesize\textbf{3}};
+        \node at (112.5:12) {\footnotesize\textbf{4}};
+        \node at (112.5:15) {\footnotesize\textbf{5}};
+
+        % Add legend at the bottom
+        \node[fill=blue!20, draw=black, align=center] at (0, -20) {\scriptsize Actual Maturity Levels};
+        \node[red, thick, dashed, draw=black, align=center] at (0, -23) {\scriptsize Target Maturity Levels};
     \end{tikzpicture}
-    \caption{Maturity Level Spider Graph}
+    \caption{Maturity Level Spider Graph with Target Levels}
     \label{fig:maturity-level-spider-graph}
@@
 
-By targeting a level just above the current one, organizations can make gradual improvements without overwhelming the staff.
-This approach helps achieve data quality benefits step by step, with clear goals along the way.
-In the end, this method leads to more manageable and effective improvements in data quality \cite{loshin_dqi}.
-
 \subsection{Recommendations}
-Gaps between the company current data quality and the target expectations through assessments or interviews is identified.
+% Gaps between the company current data quality and the target expectations through assessments or interviews is identified.
 These gaps show characteristics that are not yet implemented.
@@
 The complete gap analysis to gap analysis can be seen in Table \ref{tab:mapping}.
-The activities to improve Data Quality Management (DQM) based on the mapping to the Data Management Body of Knowledge (DMBOK) are listed below:
-\begin{enumerate}
-    \item Manage Data Quality Rules (DQM Activity 7.1) \\ Managing data quality rules means analyzing data to create rules, adding rules to system processes, and documenting them clearly.
+% The activities to improve Data Quality Management (DQM) based on the mapping to the Data Management Body of Knowledge (DMBOK) are listed below:
+% \begin{enumerate}
+%     \item Manage Data Quality Rules (DQM Activity 7.1) \\ Managing data quality rules means analyzing data to create rules, adding rules to system processes, and documenting them clearly.
 The rules should support business goals, be checked through data analysis, and confirmed by experts.
@@
 Below is a list of characteristics the company has not yet implemented, based on component maturity description of data quality management by David Loshin \cite{loshin_dqi}.
-        \begin{itemize}
-            \item "No data quality expectations have been documented"
-            \item "Expectations associated with dimensions of data quality associated with data values, formats, and semantics can be articulated using data quality rules
-            \item "Policies are informal"
-            \item 
-        \end{itemize}
-\end{enumerate}
+%         \begin{itemize}
+%             \item "No data quality expectations have been documented"
+%             \item "Expectations associated with dimensions of data quality associated with data values, formats, and semantics can be articulated using data quality rules
+%             \item "Policies are informal"
+%         \end{itemize}
+% \end{enumerate}
 
-\begin{table*}[h]
+The assessment results highlighted several gaps between the company’s current data quality management (DQM) practices and the target expectations.
+These gaps represent characteristics that have not yet been implemented and hinder the organization’s progress toward higher maturity levels.
+Recommendations are presented below, prioritized to ensure a logical sequence of improvements that align with business goals and operational feasibility.
+The detailed mapping of gaps and recommended activities to the Data Management Body of Knowledge (DMBOK) is provided in Table \ref{tab:mapping}.
+
+\begin{table*}[hbt!]
 \caption{Mapping the gaps in DQM maturity levels to the activities outlined in DQM-DMBOK}
@@
 
+The first recommendation is to formalize data quality rules as this serves as the foundation for consistent data quality practices.
+The organization should develop and document formal data quality expectations and policies while defining rules associated with data values, formats, and semantics to ensure alignment with business objectives.
+These rules must be disseminated to all data users to promote awareness and encourage compliance.
+Achieving 100% documentation coverage of these rules within six months is suggested as a measurable target.
+
+The second recommendation focuses on strengthening the data governance framework, which is essential for assigning accountability and ensuring sustained improvements.
+Establishing a formal data stewardship role or team responsible for data quality management is critical, alongside creating guiding principles, a data quality charter, and governance policies.
+A cross-functional governance workgroup should also be formed to oversee data quality initiatives.
+The organization should aim to establish this governance framework and approve the related policies within three months.
+
+Implementing data quality technology is the third recommendation.
+Advanced tools for data quality assessment and validation are necessary to automate processes and ensure real-time monitoring.
+Deploying tools for data profiling, validation, and cleansing, as well as introducing rule-based validation techniques to detect errors in real-time, will significantly improve operational efficiency.
+Additionally, technology that matches and links data across systems should be adopted.
+A 50% reduction in data errors through automated validation tools within 12 months is a key goal for this initiative.
+
+Lastly, improving performance management is essential to establish mechanisms for measuring, monitoring, and reporting data quality effectively.
+Key metrics such as data error rates, SLA adherence, and improvement trends should be defined and integrated into a data quality scorecard for regular internal and external reporting.
+These metrics should also be incorporated into the organization’s performance review process.
+Implementing these scorecards within six months and reporting monthly trends will help track progress and ensure accountability.
+
+\subsubsection{Measurable Goals and Roadmap}
+
+In the short term, the organization should focus on formalizing data quality rules and disseminating them across the organization.
+Additionally, establishing a dedicated data governance team and approving guiding policies are critical initial steps.
+These efforts will lay the groundwork for subsequent improvements.
+
+In the long term, deploying data quality tools and automating validation processes are key priorities.
+These efforts should be complemented by integrating data quality metrics into performance reviews and achieving targeted reductions in error rates.
+This phased approach ensures manageable progress and aligns with the organization’s capacity for change.
+
 \section{Conclusions and Future Works}
